---
title: "discharge for Bisley and Puente Roto vs Precip at Bisley lower tower."
author: "Miguel Leon"
date: "Thursday, April 2nd, 2015"
output:
  html_document:
    fig_width: 12
---

discharge for Bisley and Puente Roto vs Precip at Bisley lower tower

```{r, echo=FALSE, message=FALSE}

# Load the project
project_directory <- "C:/Users/leonmi/Google Drive/Discharge"# library(devtools)
#project_directory <- "C:/Users/aa20/Dropbox/Manuscripts/Composite Method/composite_client"
library(ProjectTemplate)
#source(paste0(project_directory,"/","lib/loadProject.R"))
setwd(project_directory)
source("C:/Users/leonmi/Google Drive/loadest/composite_client/src/scripts/reportHelpers.R")

# Redefine project_directory now that loadProjectFromCache has cleared the old variable
project_directory <- "C:/Users/leonmi/Google Drive/Discharge" 
#project_directory <- "C:/Users/aa20/Dropbox/Manuscripts/Composite Method/composite_client"

# Set options for producing the html filee
library(knitr)
opts_chunk$set(echo=FALSE, message=FALSE, warn=FALSE)
options(warn=-1)

# Load libraries we'll use, suppressing messages via message=FALSE option to knitr chunk
library(MASS)
library(rloadest)
library(lubridate)
library(dplyr)
library(ggplot2)

#Bis Q Day 87 to 10NoFlowRemoved.csv

newnames <- as.vector(t(read.csv(
  "Bis Q Day 87 to 10NoFlowRemoved.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

Q1FullFlow <- read.csv(
  "Bis Q Day 87 to 10NoFlowRemoved.csv",
  sep=",",header=FALSE,col.names=newnames,skip=2,stringsAsFactors=FALSE)

newnames <- as.vector(t(read.csv(
  "Quebreda (Q1) Daily 1-9-10 to4-11-11.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

Q1wDis <- read.csv(
  "Quebreda (Q1) Daily 1-9-10 to4-11-11.csv",
  sep=",",header=FALSE,col.names=newnames,skip=2,stringsAsFactors=FALSE)

newnames <- as.vector(t(read.csv(
  "Q1D_7-26-12toCurrent_0.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

Q1 <- read.csv(
  "Q1D_7-26-12toCurrent_0.csv",
  sep=",",header=FALSE,col.names=newnames,skip=3,stringsAsFactors=FALSE)

          
            

newnames <- as.vector(t(read.csv(
  "PrecipAndFlowBisley.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

PrecipAndQ <- read.csv(
  "PrecipAndFlowBisley.csv",
  sep=",",header=FALSE,col.names=newnames,skip=1,stringsAsFactors=FALSE)     

PrecipAndQ$Date <- as.POSIXct(strptime(paste(PrecipAndQ$Date,"12:00"),format="%m/%d/%Y",tz="America/Puerto_Rico"))

Q1FullFlow$Date <- as.POSIXct(strptime(paste(Q1FullFlow$Date,"12:00"),format="%m/%d/%Y",tz="America/Puerto_Rico"))


# 
# 
# ggplot() + ggtitle("Discharge mm/day") + 
#   geom_line(data= PrecipAndQ, aes(x=Date, y=Q1md , color="Mean Daily Discharge mm/day")) +
#   geom_line(data= PrecipAndQ, aes(x=Date, y=precipmmd,  color="precip per day mm/day "), alpha=0.5)
# 
# 
# ggplot() + ggtitle("Q1 Discharge mm/day") + 
#   geom_line(data= PrecipAndQ, aes(x=Date, y=Q1md ), color="sienna2")
# 
# 
# ggplot() + ggtitle("Q2 Discharge mm/day") + 
#   geom_line(data= PrecipAndQ, aes(x=Date, y=Q2md ), colour="maroon")
# 
# 
# ggplot() + ggtitle("Q3 Log Discharge mm/day") + 
#   geom_line(data= PrecipAndQ, aes(x=Date, y=Q3md ), color="chartreuse4")

ggplot() + ggtitle("Q1 Log Discharge mm/day") + 
  geom_line(data= Q1FullFlow, aes(x=Date, y=log(Q1md) ), color="sienna2")


```
Here we can clearly see the change in variability in Q1, the range of values seems to shrink. 

Let's look at log discharge for Q2 and Q3. 

```{r, echo=FALSE}

ggplot() + ggtitle("Q1 vs Q2 Log Discharge mm/day") + 
  geom_point(data= Q1FullFlow, aes(x=log(Q2md), y=log(Q1md) ), color='maroon')


ggplot() + ggtitle("Q2 vs Q3 Log Discharge mm/day") + 
  geom_point(data= Q1FullFlow, aes(x=log(Q2md), y=log(Q3md) ), color='maroon')

ggplot() + ggtitle("Q2 Log Discharge mm/day") + 
  geom_line(data= Q1FullFlow, aes(x=Date, y=log(Q2md) ), color='maroon')


ggplot() + ggtitle("Q3 Log Discharge mm/day") + 
  geom_line(data= Q1FullFlow, aes(x=Date, y=log(Q3md) ), color="chartreuse4")


ggplot() + ggtitle("Puente Roto Log Discharge mm/day") + 
  geom_line(data= Q1FullFlow, aes(x=Date, y=log(PRmd) ), color="burlywood3")


# 
# ggplot() + ggtitle("Log Precip mm/day") + 
#   geom_line(data= PrecipAndQ, aes(x=Date, y=log(precipmmd) , color="Log precip per day mm/day"))

```
Q2 might seem to have the opposite problem, but given the increase in precip in the analysis further below this is probably ok. 


The below plot Discharge Vs precip for the three gauges. 
```{r, echo=FALSE}



ggplot() + ggtitle("Q1 discharge mm/day Vs Precip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=precipmmd, y= Q1md), color="sienna2")

ggplot() + ggtitle("Q2 Log discharge mm/day Vs Precip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=precipmmd, y= Q2md), color="maroon")

ggplot() + ggtitle("Q3 discharge mm/day VsPrecip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=precipmmd, y=Q3md ), color="chartreuse4")

ggplot() + ggtitle("Puente Roto discharge mm/day VsPrecip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=precipmmd, y=PRmd ), color="burlywood3")
```
This is hard to see let's limit the x y range to take some of the outliers out of view. 

```{r, echo=FALSE}
ggplot() + ggtitle("Q1 discharge mm/day Vs Precip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=precipmmd, y= Q1md), color="sienna2")+ylim(0,100)+xlim(0,150)

ggplot() + ggtitle("Q2 Log discharge mm/day Vs Precip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=precipmmd, y= Q2md), color="maroon")+ylim(0,100)+xlim(0,150)

ggplot() + ggtitle("Q3 discharge mm/day VsPrecip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=precipmmd, y=Q3md ), color="chartreuse4")+ylim(0,100)+xlim(0,150)

ggplot() + ggtitle("Puente Roto discharge mm/day VsPrecip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=precipmmd, y=PRmd ), color="burlywood3")+ylim(0,100)+xlim(0,150)
```
Maybe looking at log v log might help? 

```{r, echo=FALSE}

ggplot() + ggtitle("Q1 Log discharge mm/day Vs Log Precip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=log(precipmmd), y= log(Q1md)), color="sienna2")

ggplot() + ggtitle("Q2 Log discharge mm/day Vs Log Precip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=log(precipmmd), y= log(Q2md)), color="maroon")

ggplot() + ggtitle("Q3 Log discharge mm/day Vs Log Precip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=log(precipmmd), y=log(Q3md) ), color="chartreuse4")

ggplot() + ggtitle("Puente Roto Log discharge mm/day Vs Log Precip mm/day") + 
  geom_point(data= PrecipAndQ, aes(x=log(precipmmd), y=log(PRmd) ), color="burlywood3")

  
startDate <- as.POSIXct("2005-06-24") 
#endDate <- as.POSIXct("2012-01-01")

PrecipAndQ<- transform(PrecipAndQ, YR=as.numeric(format(Date, "%Y")))


PrecipAndQNewer <- PrecipAndQ[PrecipAndQ$Date >=  startDate ,]
PrecipAndQOlder <- PrecipAndQ[PrecipAndQ$Date <  startDate ,]
```
Use Q2 and Precip to predict Q1 

```{r, echo=FALSE}

PrecipAndQOlder$Q2mdlog <- log(PrecipAndQOlder$Q2md)
PrecipAndQOlder <- PrecipAndQOlder[!is.na(PrecipAndQOlder$Q2mdlog),]

PrecipAndQOlder$Q1mdlog <- log(PrecipAndQOlder$Q1md)
PrecipAndQOlder <- PrecipAndQOlder[!is.na(PrecipAndQOlder$Q1mdlog),]


Q1Model<- lm( Q1md~ Q2md+Q2mdlog+ precipmmd+log(precipmmd), PrecipAndQOlder)
summary(Q1Model)
Q1Predicted <- predict(Q1Model,PrecipAndQNewer,se.fit=TRUE)

PrecipAndQNewer$fitQ1 <- Q1Predicted$fit
PrecipAndQNewer$Q1se <-  Q1Predicted$se.fit

ggplot() + ggtitle("Predicted Q1 Log Discharge mm/day") + 
  geom_line(data= PrecipAndQNewer, aes(x=Date, y=log(fitQ1) , color="predicted "))+
   #geom_errorbar(data= PrecipAndQNewer, aes(ymin=fitQ1-log(Q1se), ymax=fitQ1+log(Q1se), x=Date), width=.1) +
  geom_line(data= PrecipAndQOlder, aes(x=Date, y=log(Q1md) , color="Old recorded data that should be good"))


ggplot() + ggtitle("Predicted Q1 Discharge mm/day") + 
  geom_point(data= PrecipAndQNewer, aes(x=Date, y=fitQ1 , color="predicted "))+
  # geom_errorbar(data= PrecipAndQNewer, aes(ymin=fitQ1-(2*Q1se), ymax=fitQ1+(2*Q1se), x=Date), width=.1) +
  geom_point(data= PrecipAndQOlder, aes(x=Date, y=Q1md , color="Old recorded data that should be good"))

ggplot() + ggtitle(" Q1 Log vs Q2 Log Discharge mm/day") + 
  geom_point(data= PrecipAndQNewer, aes(x=log(Q2md), y=log(fitQ1) , color="predicted "))+
  geom_point(data= PrecipAndQOlder, aes(x=log(Q2md), y=log(Q1md) , color="Old recorded data that should be good"))

ggplot() + ggtitle("Predicted Q1 Log Discharge mm/day vs recorded values") + 
  geom_line(data= PrecipAndQNewer, aes(x=Date, y=log(fitQ1) , color="predicted "))+
  geom_line(data= PrecipAndQNewer, aes(x=Date, y=log(Q1md) , color="recorded data we want to replace"), alpha=.5)

```
Q1 SD then Summary of precipitation at bisley lower tower in mm/day before 2005-06-24

```{r, echo=FALSE}

#compute means and sds 

sdPrecipOlder<- sd(PrecipAndQOlder$precipmmd,na.rm=TRUE)
sdPrecipOlder
summary(PrecipAndQOlder$precipmmd)
```
Q1 SD then Summary of precipitation at bisley lower tower in mm/day after 2005-06-24

```{r, echo=FALSE}
sdPrecipNewer<- sd(PrecipAndQNewer$precipmmd,na.rm=TRUE)
sdPrecipNewer
summary(PrecipAndQNewer$precipmmd)

```
Precip increases after 2005-06-24 and the standard deviation for precip also increases.

Q1 SD then Summary of discharge at Q1 in mm/day before 2005-06-24

```{r, echo=FALSE}
sdQ1mdOlder<- sd(PrecipAndQOlder$Q1md,na.rm=TRUE)
sdQ1mdOlder
summary(PrecipAndQOlder$Q1md,na.rm=TRUE)

```
Q1 SD then Summary of discharge at Q1 in mm/day after 2005-06-24

```{r, echo=FALSE}
sdQ1mdNewer<- sd(PrecipAndQNewer$Q1md,na.rm=TRUE)
sdQ1mdNewer
summary(PrecipAndQNewer$Q1md,na.rm=TRUE)
# 
# ggplot() + ggtitle("Log Discharge CFS after 2006-09-01") + 
#   geom_line(data= PrecipAndQNewer, aes(x=Date, y=log(Q1md) , color="Mean Daily Discharge mm/day"))
# 
# ggplot() + ggtitle("Discharge CFS after 2006-09-01") + 
#   geom_line(data= PrecipAndQNewer, aes(x=Date, y=Q1md , color="Mean Daily Discharge mm/day")) +
#   geom_line(data= PrecipAndQNewer, aes(x=Date, y=precipmmd,  color=" precip per day mm/day "), alpha=0.5)+ylim(0,175)
# 
# 
# ggplot() + ggtitle("Log Discharge CFS before 2006-09-01") + 
#   geom_line(data= PrecipAndQOlder, aes(x=Date, y=log(Q1md) , color="Mean Daily Discharge mm/day"))
# 
# 
# ggplot() + ggtitle("Discharge CFS before 2006-09-01") + 
#   geom_line(data= PrecipAndQOlder, aes(x=Date, y=Q1md , color="Mean Daily Discharge mm/day")) +
#   geom_line(data= PrecipAndQOlder, aes(x=Date, y=precipmmd,  color=" precip per day mm/day "), alpha=0.5) +ylim(0,175)

```
 The standard deviation of discharge decreases after  2005-06-24, while it had increased for precip, this is the problem we are seeing in the very first graph.  

```{r, echo=FALSE}

#totalCF15m


#totalCF15m2Curr

