---
title: "discharge for Bisley Q1."
author: "Miguel Leon"
date: "Tuesday, April 7th, 2015"
output:
  html_document:
    fig_width: 12
---

discharge for Bisley Q1

```{r, echo=FALSE, message=FALSE}

# Load the project
project_directory <- "C:/Users/leonmi/Google Drive/Discharge"# library(devtools)
#project_directory <- "C:/Users/aa20/Dropbox/Manuscripts/Composite Method/composite_client"
library(ProjectTemplate)
#source(paste0(project_directory,"/","lib/loadProject.R"))
setwd(project_directory)
source("C:/Users/leonmi/Google Drive/loadest/composite_client/src/scripts/reportHelpers.R")

# Redefine project_directory now that loadProjectFromCache has cleared the old variable
project_directory <- "C:/Users/leonmi/Google Drive/Discharge" 
#project_directory <- "C:/Users/aa20/Dropbox/Manuscripts/Composite Method/composite_client"

# Set options for producing the html filee
library(knitr)
opts_chunk$set(echo=FALSE, message=FALSE, warn=FALSE)
options(warn=-1)

# Load libraries we'll use, suppressing messages via message=FALSE option to knitr chunk
library(MASS)
library(rloadest)
library(lubridate)
library(dplyr)
library(ggplot2)

#Bis Q Day 87 to 10NoFlowRemoved.csv

newnames <- as.vector(t(read.csv(
  "Bis Q Day 87 to 10NoFlowRemoved.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

Q1FullFlow <- read.csv(
  "Bis Q Day 87 to 10NoFlowRemoved.csv",
  sep=",",header=FALSE,col.names=newnames,skip=2,stringsAsFactors=FALSE)

newnames <- as.vector(t(read.csv(
  "Quebreda (Q1) Daily 1-9-10 to4-11-11.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

Q1wDis <- read.csv(
  "Quebreda (Q1) Daily 1-9-10 to4-11-11.csv",
  sep=",",header=FALSE,col.names=newnames,skip=2,stringsAsFactors=FALSE)

newnames <- as.vector(t(read.csv(
  "Q1D_7-26-12toCurrent_0.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

Q1 <- read.csv(
  "Q1D_7-26-12toCurrent_0.csv",
  sep=",",header=FALSE,col.names=newnames,skip=3,stringsAsFactors=FALSE)

model<- lm( Discharge~ Level+Level^2+exp(Level)+log(Level), Q1wDis)
            
 #Q1_current 1-8-10 to 4-11-11_0.csv           

newnames <- as.vector(t(read.csv(
  "Q12014.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

Q12014 <- read.csv(
  "Q12014.csv",
  sep=",",header=FALSE,col.names=newnames,skip=1,stringsAsFactors=FALSE)
Q12014$mm.day <- as.numeric(Q12014$mm.day)


newnames <- as.vector(t(read.csv(
  "Q1_current 1-8-10 to 4-11-11_0.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

Q12010 <- read.csv(
  "Q1_current 1-8-10 to 4-11-11_0.csv",
  sep=",",header=FALSE,col.names=newnames,skip=1,stringsAsFactors=FALSE)

Q12010$mm.day <- as.numeric(Q12010$NA.)

newnames <- as.vector(t(read.csv(
  "PrecipAndFlowBisley.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

PrecipAndQ <- read.csv(
  "PrecipAndFlowBisley.csv",
  sep=",",header=FALSE,col.names=newnames,skip=1,stringsAsFactors=FALSE)     

PrecipAndQ$Date <- as.POSIXct(strptime(paste(PrecipAndQ$Date,"12:00"),format="%m/%d/%Y",tz="America/Puerto_Rico"))

Q1FullFlow$Date <- as.POSIXct(strptime(paste(Q1FullFlow$Date,"12:00"),format="%m/%d/%Y",tz="America/Puerto_Rico"))

Q12010$Date <- as.POSIXct(strptime(Q12010$Date,format="%m/%d/%Y %H:%M",tz="America/Puerto_Rico"))

Q12014$Date <- as.POSIXct(strptime(Q12014$TS,format="%m/%d/%Y %H:%M",tz="America/Puerto_Rico"))

  Q12014 <-Q12014[order(Q12014$Date),]

  Q12010 <-Q12010[order(Q12010$Date),]


Q12014$Day<- as.POSIXct(strptime(Q12014$TS,format="%m/%d/%Y",tz="America/Puerto_Rico"))

#FILL IN DISCHARGE MEAN FOR ALL TIMES 
Q12014<- Q12014 %>%
  group_by(Day) %>% 
  mutate(DISCHARGE_MEAN=mean(mm.day,na.rm=TRUE))
days<- list(Q12014$Day)
Q12014day<- aggregate(Q12014,by=days, FUN=head, 1)
Q12014day<- transform(Q12014day, YR=as.numeric(format(Date, "%Y")))
years<- list(Q12014day$YR)
Q12014yr<- aggregate(Q12014day$DISCHARGE_MEAN,by=years, FUN=sum)

# 
# 
# ggplot() + ggtitle("Discharge mm/day") + 
#   geom_line(data= PrecipAndQ, aes(x=Date, y=Q1md , color="Mean Daily Discharge mm/day")) +
#   geom_line(data= PrecipAndQ, aes(x=Date, y=precipmmd,  color="precip per day mm/day "), alpha=0.5)
# 
# 
# ggplot() + ggtitle("Q1 Discharge mm/day") + 
#   geom_line(data= PrecipAndQ, aes(x=Date, y=Q1md ), color="sienna2")
# 
# 
# ggplot() + ggtitle("Q2 Discharge mm/day") + 
#   geom_line(data= PrecipAndQ, aes(x=Date, y=Q2md ), colour="maroon")
# 
# 
# ggplot() + ggtitle("Q3 Log Discharge mm/day") + 
#   geom_line(data= PrecipAndQ, aes(x=Date, y=Q3md ), color="chartreuse4")



startDate <- as.POSIXct("2009-01-01") 
endDate <- as.POSIXct("2010-01-01")

PrecipAndQ<- transform(PrecipAndQ, YR=as.numeric(format(Date, "%Y")))
Q12014$mm.day <- as.numeric(Q12014$mm.day)


PrecipAndQNewer <- PrecipAndQ[PrecipAndQ$Date >=  startDate & PrecipAndQ$Date <  endDate,]


years<- list(PrecipAndQ$YR)

Q1yrmmday<- aggregate(PrecipAndQ$Q1md,by=years, FUN=sum, na.rm=TRUE)
Toweryrmmday<- aggregate(PrecipAndQ$precipmmd,by=years, FUN=sum, na.rm=TRUE)

startDate <- as.POSIXct("2005-06-24")
PrecipAndQOlder <- PrecipAndQ[PrecipAndQ$Date <  startDate ,]



Q12010 <- Q12010[Q12010$Date <  endDate ,]

sdQ1mdOlder<- sd(PrecipAndQOlder$Q1md,na.rm=TRUE)
sdQ1mdNewer<- sd(PrecipAndQNewer$Q1md,na.rm=TRUE)
# PrecipAndQNewer$upperBound <- PrecipAndQNewer$Q1md + 2*sdQ1mdNewer
# PrecipAndQNewer$lowerBound <- PrecipAndQNewer$Q1md - 2*sdQ1mdNewer
# PrecipAndQOlder$upperBound <- PrecipAndQOlder$Q1md + 2*sdQ1mdOlder
# PrecipAndQOlder$lowerBound <- PrecipAndQOlder$Q1md - 2*sdQ1mdOlder

startDate <- as.POSIXct("2014-04-01")
endDate <- as.POSIXct("2014-07-01")
Q12014day <- Q12014day[Q12014day$Day >  startDate & Q12014day$Day <  endDate,]

ggplot() + ggtitle("Q1 daily average Wier worksheet derived Discharge mm/day") + 
  geom_line(data= Q12014day, aes(x=Day, y=DISCHARGE_MEAN), color="chartreuse4")

# 
# 
# ggplot() + ggtitle("Q1 Daily Discharge mm/day") + 
#   geom_line(data= PrecipAndQNewer, aes(x=Date, y=Q1md ), color="sienna2")
# 
# ggplot() + ggtitle("Q1 Daily Log Discharge mm/day") + 
#   geom_line(data= PrecipAndQNewer, aes(x=Date, y=log(Q1md) ), color="sienna2")
# 
# ggplot() + ggtitle("Q1 5 minute 2010 Discharge mm/day") + 
#   geom_line(data= Q12010, aes(x=Date, y=mm.day), color="maroon")
# 
# ggplot() + ggtitle("Q1 5 minute 2010 Log Discharge mm/day") + 
# #   geom_line(data= Q12010, aes(x=Date, y=log(mm.day) ), color="maroon")
# 
# ggplot() + ggtitle("Q1 5 minute Wier worksheet derived Discharge mm/day") + 
#   geom_line(data= Q12014, aes(x=Date, y=mm.day), color="chartreuse4")
# 
# 
# ggplot() + ggtitle("Q1 5 minute Wier worksheet derived Log Discharge mm/day") + 
#   geom_line(data= Q12014, aes(x=Date, y=log(mm.day) ), color="chartreuse4")

```
Precip per year

```{r, echo=FALSE}
Toweryrmmday

```
mm discharge per year

```{r, echo=FALSE}
Q1yrmmday
```
mm discharge per year with weir calculation. 

```{r, echo=FALSE}
Q12014yr

#day per year precip and Puente Roto 
PrecipAndQ$num <- 1
PrecipAndQ<- transform(PrecipAndQ, YR=as.numeric(format(Date, "%Y")))
PrecipAndQ<- PrecipAndQ[!is.na(PrecipAndQ$PRmd),]
daypYr <- with(PrecipAndQ, tapply(num, YR, sum))
daypYr

Q1FullFlow$num <- 1
Q1FullFlow<- transform(Q1FullFlow, YR=as.numeric(format(Date, "%Y")))
Q1FullFlow<- transform(Q1FullFlow, MonthYR=as.numeric(format(Date, "%Y%m")))
PrecipAndQ<- Q1FullFlow[!is.na(Q1FullFlow$PRmd),]

# daypYr <- with(Q1FullFlow, tapply(num, YR, sum))
# daypYr
# daypMth <- with(Q1FullFlow, tapply(num, MonthYR, sum))
# daypMth$dayMth <-cbind(colnames(daypMth), daypMth)

# # 
# ggplot() + ggtitle("day per month") + 
#   geom_line(data= daypMth,  aes(x=x, y=y ),color="sienna2")





# 
# ```
# Q1 SD then Summary of precipitation at bisley lower tower in mm/day before 2005-06-24
# 
# ```{r, echo=FALSE}
# 
# #compute means and sds 
# 
# sdPrecipOlder<- sd(PrecipAndQOlder$precipmmd,na.rm=TRUE)
# sdPrecipOlder
# summary(PrecipAndQOlder$precipmmd)
# ```
# Q1 SD then Summary of precipitation at bisley lower tower in mm/day after 2005-06-24
# 
# ```{r, echo=FALSE}
# sdPrecipNewer<- sd(PrecipAndQNewer$precipmmd,na.rm=TRUE)
# sdPrecipNewer
# summary(PrecipAndQNewer$precipmmd)
# 
# ```
# Precip increases after 2005-06-24 and the standard deviation for precip also increases.
# 
# Q1 SD then Summary of discharge at Q1 in mm/day before 2005-06-24
# 
# ```{r, echo=FALSE}
# 
# sdQ1mdOlder
# summary(PrecipAndQOlder$Q1md,na.rm=TRUE)
# 
# ```
# Q1 SD then Summary of discharge at Q1 in mm/day after 2005-06-24
# 
# ```{r, echo=FALSE}
# 
# sdQ1mdNewer
# summary(PrecipAndQNewer$Q1md,na.rm=TRUE)
# 
# ggplot() + ggtitle("Log Discharge CFS after 2006-09-01") + 
#   geom_line(data= PrecipAndQNewer, aes(x=Date, y=log(Q1md) , color="Mean Daily Discharge mm/day"))
# 
# ggplot() + ggtitle("Discharge CFS after 2006-09-01") + 
#   geom_line(data= PrecipAndQNewer, aes(x=Date, y=Q1md , color="Mean Daily Discharge mm/day")) +
#   geom_line(data= PrecipAndQNewer, aes(x=Date, y=precipmmd,  color=" precip per day mm/day "), alpha=0.5)+ylim(0,175)
# 
# 
# ggplot() + ggtitle("Log Discharge CFS before 2006-09-01") + 
#   geom_line(data= PrecipAndQOlder, aes(x=Date, y=log(Q1md) , color="Mean Daily Discharge mm/day"))
# 
# 
# ggplot() + ggtitle("Discharge CFS before 2006-09-01") + 
#   geom_line(data= PrecipAndQOlder, aes(x=Date, y=Q1md , color="Mean Daily Discharge mm/day")) +
#   geom_line(data= PrecipAndQOlder, aes(x=Date, y=precipmmd,  color=" precip per day mm/day "), alpha=0.5) +ylim(0,175)
# 
# ```
#  The standard deviation of discharge decreases after  2005-06-24, while it had increased for precip, this is the problem we are seeing in the graph.  
