---
title: "MPR filtered discharge"
author: "Miguel Leon"
date: "Monday, April 21, 2015"
output:
  html_document:
    fig_width: 10
---


```{r, echo=FALSE, message=FALSE}


# Load the project
project_directory <- "C:/Users/leonmi/Google Drive/Discharge" # library(devtools)
#project_directory <- "C:/Users/aa20/Dropbox/Manuscripts/Composite Method/composite_client"
library(ProjectTemplate)
#source(paste0(project_directory,"/","lib/loadProject.R"))
setwd(project_directory)
#source("C:/Users/leonmi/Google Drive/loadest/composite_client/src/scripts/reportHelpers.R")

# Redefine project_directory now that loadProjectFromCache has cleared the old variable
project_directory <- "C:/Users/leonmi/Google Drive/Discharge" 
#project_directory <- "C:/Users/aa20/Dropbox/Manuscripts/Composite Method/composite_client"

# Set options for producing the html filee
library(knitr)
opts_chunk$set(echo=FALSE, message=FALSE, warn=FALSE)
options(warn=-1)

# Load libraries we'll use, suppressing messages via message=FALSE option to knitr chunk
library(MASS)
library(rloadest)
library(lubridate)
library(dplyr)
library(ggplot2)
library(data.table)
#MPRDischargeFrom1999
insertRow <- function(existingDF, newrow, r) {
  existingDF[seq(r+1,nrow(existingDF)+1),] <- existingDF[seq(r,nrow(existingDF)),]
  existingDF[r,] <- newrow
  existingDF
}
#MPRDailyExport_KC.csv
# 
# newnames <- as.vector(t(read.csv(
#   "MPRDailyExport_KC.csv",
#   sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))
# 
# MPRDateFormat <- read.csv(
#   "MPRDailyExport_KC.csv",
#   sep=",",header=FALSE,col.names=newnames,skip=1,stringsAsFactors=FALSE)
# MPRDateFormat$Date <- as.POSIXct(strptime(MPRDateFormat$Day ,format="%m/%d/%Y",tz="America/Puerto_Rico"))
# write.csv(MPRDateFormat,
#     "./MPRDateFormat.csv",na="NA",,row.names=TRUE)

newnames <- as.vector(t(read.csv(
  "MPRDischarge.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

MPRFullFlow <- read.csv(
  "MPRDischarge.csv",
  sep=",",header=FALSE,col.names=newnames,skip=1,stringsAsFactors=FALSE)

newnames <- as.vector(t(read.csv(
  "MPRDischargeFrom1997.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

MPRFrom1997 <- read.csv(
  "MPRDischargeFrom1997.csv",
  sep=",",header=FALSE,col.names=newnames,skip=1,stringsAsFactors=FALSE)

newnames <- as.vector(t(read.csv(
  "MPRDischargeFrom2006.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

MPRFrom2006 <- read.csv(
  "MPRDischargeFrom2006.csv",
  sep=",",header=FALSE,col.names=newnames,skip=1,stringsAsFactors=FALSE)

newnames <- as.vector(t(read.csv(
  "DailyDischargeUSGS.csv",
  sep=",",header=FALSE,skip=0,nrows=1,stringsAsFactors=FALSE)[1,]))

USGSDischarge <- read.csv(
  "DailyDischargeUSGS.csv",
  sep=",",header=FALSE,col.names=newnames,skip=1,stringsAsFactors=FALSE)






USGSDischarge$Date <- as.POSIXct(strptime(USGSDischarge$Date  ,format="%m/%d/%Y"))

MPRFullFlow$DateTime <- as.POSIXct(strptime(MPRFullFlow$DateTime ,format="%m/%d/%Y %H:%M",tz="America/Puerto_Rico"))


MPRFrom1997$DateTime <- as.POSIXct(strptime(MPRFrom1997$DateTime ,format="%m/%d/%Y %H:%M",tz="America/Puerto_Rico"))

MPRFrom2006$DateTime <- as.POSIXct(strptime(MPRFrom2006$DateTime ,format="%m/%d/%Y %H:%M",tz="America/Puerto_Rico"))

MPRFullFlow<- merge(MPRFullFlow,MPRFrom1997,all=TRUE)
MPRFullFlow<- merge(MPRFullFlow,MPRFrom2006,all=TRUE)
#remove NA values 
MPRFullFlow <- MPRFullFlow[!is.na(MPRFullFlow$USGS_cfps),]
MPRFullFlow<- MPRFullFlow[order(MPRFullFlow$DateTime),]
  

MPRFullFlow$num <- 1
min15pyr <- with(MPRFullFlow, tapply(num, YEAR, sum))

```

15 minute (or 10 min) records per year

```{r, echo=FALSE, message=FALSE}

min15pyr

dt <- as.POSIXlt("1986-10-01 00:15:00")
dt <- dt -900
newrow <- list(1986,1,as.POSIXct(strptime(dt, format="%Y-%m-%d",tz="America/Puerto_Rico")),NA,NA,1986,1) #%H:%M:%S

#,origin = "1900-01-01"
#"1999-10-01 00:00:00","%Y-%m-%d %H:%M:%S",tz="America/Puerto_Rico"
#USGS_Sonadora_IDA2 <- rbind(USGS_Sonadora_IDA, newrow)
MPRFullFlow<- insertRow(MPRFullFlow, newrow, 1)

MPRFullFlow$diffsec <- c(NA, tail(MPRFullFlow$DateTime, -1) - head(MPRFullFlow$DateTime, -1))
MPRFullFlow$diffMin <- MPRFullFlow$diffsec / 60

#MPRFullFlow<-MPRFullFlow[!MPRFullFlow$diffMin ==10,]
# 
#   ggplot() + ggtitle("MPR log Discharge CFS") + 
#     geom_point(data= MPR10, aes(x=DateTime, y=log(USGS_cfps) , color="Mean Daily Discharge"))

#MPRFullFlow<-MPRFullFlow[!MPRFullFlow$diffMin ==10,]
#MPRFullFlow<-MPRFullFlow[!MPRFullFlow$diffMin ==5,]

MPRFullFlow$diffsec[MPRFullFlow$diffsec > 900] <- 900
MPRFullFlow$diffMin[MPRFullFlow$diffMin > 15] <- 15

#some of these are 5 minute not 15 minute need to make sure the cfps for each record represents the right amount of time. 
totalCF15mCurr<- with(MPRFullFlow, tapply(((USGS_cfps*diffsec)), YEAR, sum))
totalCF15m2Curr <- totalCF15mCurr /with(MPRFullFlow, tapply(((diffsec)), YEAR, sum))

#totalCF15m2Curr
# write.csv(totalCF15m2Curr,
#     "./MPRMeanAnnualDischarge.csv",na="NA",,row.names=TRUE)

#agggregate by day 


#calculate mean daily discharge



MPRFullFlow$Day<- format(MPRFullFlow$DateTime, "%m/%d/%Y") 

#FILL IN DISCHARGE MEAN FOR ALL TIMES 
MPRFullFlow<- MPRFullFlow %>%
  group_by(Day) %>% 
  mutate(cfsps_day_mean=mean(USGS_cfps,na.rm=TRUE))
days<- list(MPRFullFlow$Day)
MPRFullFlowDaily<- aggregate(MPRFullFlow,by=days, FUN=head, 1)

#write daily discharge to a file 
# write.csv(MPRFullFlowDaily,
#     "./MPRDailyExport.csv",na="NA",,row.names=FALSE)


```

compare daily flows USGS vs Jody's 

```{r, echo=FALSE, message=FALSE}

startDate <- as.POSIXct("2006-01-01") 
endDate <- as.POSIXct("2014-11-23")

MPRFullFlow2<- MPRFullFlow[MPRFullFlow$DateTime >  startDate 
                        & MPRFullFlow$DateTime < endDate,]

MPRFullFlowDaily2<- MPRFullFlowDaily[MPRFullFlowDaily$DateTime >  startDate 
                        & MPRFullFlowDaily$DateTime < endDate,]

USGSDischarge2<- USGSDischarge[USGSDischarge$Date >  startDate 
                        & USGSDischarge$Date < endDate,]
MPRFullFlowDaily2$Date <- as.POSIXct(MPRFullFlowDaily2$Day,format="%m/%d/%Y")


  ggplot() + ggtitle("discharge") + 
   geom_line(data=MPRFullFlowDaily2 , aes(x=Date, y=cfsps_day_mean , color="Mean Daily Discharge calculated from Jody"),alpha=.5)+
  geom_line(data=USGSDischarge2 , aes(x=Date, y=cfs , color="Mean Daily Discharge USGS"),alpha=.5)


mergeflow<-merge(USGSDischarge2,MPRFullFlowDaily2,  by="Date") #, incomparables

# 
# mergeflow<- data.frame(USGSMeanDis=USGSDischarge2$cfs,JodyMeanDis=MPRFullFlowDaily2$cfsps_day_mean, 
#                        Date=MPRFullFlowDaily2[match(USGSDischarge2$Date,MPRFullFlowDaily2$Date),])

mergeflow<- mergeflow[order(as.Date(mergeflow$Date, format="%d/%m/%Y")),]


  ggplot() + ggtitle("merged discharge") + 
       geom_line(data= mergeflow, aes(x=Date, y=cfs , color="Mean Daily Discharge USGS"))+
   geom_line(data=mergeflow , aes(x=DateTime, y=cfsps_day_mean , color="Mean Daily Discharge"),alpha=.5)

#find values from jody and USGS which are close together. 
sdUSGS <- sd(mergeflow$cfs)
#sd is too large 
mergeflow$cfsmprUSGS<-mergeflow$cfs
mergeflow$cfsmprJody<- mergeflow$cfsps_day_mean
mergeflow$DischargeDiff <- mergeflow$cfsmprUSGS / mergeflow$cfsmprJody
```

number of daily mean values  

```{r, echo=FALSE, message=FALSE}

nrow(mergeflow)

mergeflowClose <- mergeflow[mergeflow$DischargeDiff>=.95 & mergeflow$DischargeDiff<=1.05,]
mergeflowClose<- mergeflowClose[c("Date","cfsmprUSGS","cfsmprJody","DischargeDiff")]
```

number of daily mean values where the mean daily discharge from Jody's 15 min record are within 5% of the reported USGS values  

```{r, echo=FALSE, message=FALSE}

nrow(mergeflowClose)

#find 15 minute records which match the selected daily records. 
```

number of 15 min records within the date range  2006-01-01 to 2014-11-23


```{r, echo=FALSE, message=FALSE}
nrow(MPRFullFlow2)

MPRFullFlow2$Date<- as.POSIXct(MPRFullFlow2$Day,format="%m/%d/%Y")

#MPRFullFlow2 <- MPRFullFlow[MPRFullFlow$Date == mergeflowClose$Date,]
MPRFullFlow2<-merge(MPRFullFlow2,mergeflowClose,  by="Date")
MPRFullFlow2<- MPRFullFlow2[order(MPRFullFlow2$DateTime),]

MPRFullFlow2$cfsUSGS_mean_daily<-MPRFullFlow2$cfsmprUSGS
MPRFullFlow2$cfsFromJody_mean_daily<-MPRFullFlow2$cfsmprJody

MPRFullFlow2<- MPRFullFlow2[c("DateTime","USGS_cfps","USGS_STAGE","cfsUSGS_mean_daily","cfsFromJody_mean_daily")]

```

number of 15 min records matching dates selected where the computed mean daily discharge records are within 5% 


```{r, echo=FALSE, message=FALSE}
nrow(MPRFullFlow2)


write.csv(MPRFullFlow2,
     "./CloseDischarge15minFromJody.csv",na="NA",,row.names=TRUE)

  ggplot() + ggtitle("merged discharge values from Jody within 5%") + 
       geom_point(data= mergeflowClose, aes(x=Date, y=cfsmprUSGS , color="Mean Daily Discharge USGS"))+
   geom_point(data=mergeflowClose , aes(x=Date, y=cfsmprJody , color="Mean Daily Discharge"),alpha=.5)



  ggplot() + ggtitle("log of merged discharge values from Jody within 5% of USGS") + 
       geom_point(data= mergeflowClose, aes(x=Date, y=log(cfsmprUSGS) , color="Mean Daily Discharge USGS"))+
   geom_point(data=mergeflowClose , aes(x=Date, y=log(cfsmprJody) , color="Mean Daily Discharge"),alpha=.5)

startDate <- as.POSIXct("2006-01-01") 
endDate <- as.POSIXct("2007-01-01")

mergeflowClose2<- mergeflowClose[mergeflowClose$Date >  startDate 
                        & mergeflowClose$Date < endDate,]


  ggplot() + ggtitle("MPR Discharge CFS 2006; merged discharge values from Jody within 5% of USGS") + 
       geom_line(data= mergeflowClose2, aes(x=Date, y=cfsmprUSGS , color="Mean Daily Discharge USGS"))+
   geom_line(data=mergeflowClose2 , aes(x=Date, y=cfsmprJody , color="Mean Daily Discharge"),alpha=.5)

startDate <- as.POSIXct("2007-01-01") 
endDate <- as.POSIXct("2008-01-01")

mergeflowClose2<- mergeflowClose[mergeflowClose$Date >  startDate 
                        & mergeflowClose$Date < endDate,]


  ggplot() + ggtitle("MPR Discharge CFS 2007; merged discharge values from Jody within 5% of USGS") + 
       geom_point(data= mergeflowClose2, aes(x=Date, y=cfsmprUSGS , color="Mean Daily Discharge USGS"))+
   geom_point(data=mergeflowClose2 , aes(x=Date, y=cfsmprJody , color="Mean Daily Discharge"),alpha=.5)

startDate <- as.POSIXct("2008-01-01") 
endDate <- as.POSIXct("2009-01-01")

mergeflowClose2<- mergeflowClose[mergeflowClose$Date >  startDate 
                        & mergeflowClose$Date < endDate,]


  ggplot() + ggtitle("MPR Discharge CFS 2008; merged discharge values from Jody within 5% of USGS ") + 
       geom_point(data= mergeflowClose2, aes(x=Date, y=cfsmprUSGS , color="Mean Daily Discharge USGS"))+
   geom_point(data=mergeflowClose2 , aes(x=Date, y=cfsmprJody , color="Mean Daily Discharge"),alpha=.5)


startDate <- as.POSIXct("2009-01-01") 
endDate <- as.POSIXct("2010-01-01")

mergeflowClose2<- mergeflowClose[mergeflowClose$Date >  startDate 
                        & mergeflowClose$Date < endDate,]


  ggplot() + ggtitle("MPR Discharge CFS 2009; merged discharge values from Jody within 5% of USGS ") + 
       geom_line(data= mergeflowClose2, aes(x=Date, y=cfsmprUSGS , color="Mean Daily Discharge USGS"))+
   geom_line(data=mergeflowClose2 , aes(x=Date, y=cfsmprJody , color="Mean Daily Discharge"),alpha=.5)


write.csv(mergeflowClose,
     "./CloseDischargeUSGSJody.csv",na="NA",,row.names=TRUE)

